Notes on Prediction Types

### 2011-06-17 docs/pert_notes/pert.tex
finish the update for now.
species_pred_type = 3 is not listed here.

Here we wish to construct $\left [ (\rho h)_0 + (\rho
  h)'_\mathrm{edge} \right ]$ by predicting $(\rho h)'$ to the edges.

@@

For spherical, however, instead of computing $(\rho h)_0$ to edges
directly, we compute $\rho_0$ and $h_0$ separately at the edges, and
multiply to get $(\rho h)_0$.

@@

We use the same procedure described in Section \ref{Computing rho at
  edges} to computing $\rho_\mathrm{edge}$ from $\rho_0$ and
$\rho'_\mathrm{edge}$ and then multiply by $h_\mathrm{edge}$.

@@

We the use EOS in {\tt makeHfromRhoT\_edge} (called from {\tt
  enthalpy\_advance}) to convert from $T_\mathrm{edge}$ to $(\rho
h)'_\mathrm{edge}$.  For the EOS call, we need $X_\mathrm{edge}$ and
$\rho_\mathrm{edge}$.  This construction depends on {\tt
  species\_pred\_type}, since the species edge states may differ
between the various prediction types (see the ``species quantity''
column in table~\ref{table:pred:hoverview}).  The EOS inputs are
constructed as:

@@

The output of  {\tt makeHfromRhoT\_edge} is $(\rho h)'_\mathrm{edge}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advancing $\rho h$}
We update the enthalpy analogously to the species update in 
Section \ref{Advancing rhoX_k}.  The forcing term does not include reaction
source terms accounted for in {\bf React State}.
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = 
-\nabla\cdot\left\{\left[(\rho h)_0^{n+\myhalf,{\rm avg}} 
+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} + \psi  \enskip .
\end{equation}

>>>>

Here we wish to construct $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho
  h)'_\mathrm{edge} \right ]$ by predicting $(\rho h)'$ to the edges.

@@

For spherical, however, instead of computing $(\rho h)_0$ on edges
directly, we compute $\rho_0$ and $h_0$ separately at the edges, and
multiply to get $(\rho h)_0$.

@@

We use the same procedure described in Section \ref{Computing rho at
  edges} for computing $\rho_\mathrm{edge}$ from $\rho_0$ and
$\rho'_\mathrm{edge}$ and then multiply by $h_\mathrm{edge}$.

@@

We call the EOS in {\tt makeHfromRhoT\_edge} (called from {\tt
  enthalpy\_advance}) to convert from $T_\mathrm{edge}$ to $(\rho
h)'_\mathrm{edge}$.  For the EOS call, we need $X_\mathrm{edge}$ and
$\rho_\mathrm{edge}$.  This construction depends on {\tt
  species\_pred\_type}, since the species edge states may differ
between the various prediction types (see the ``species quantity''
column in table~\ref{table:pred:hoverview}).  The EOS inputs are
constructed as:

@@

After calling the EOS, the output of {\tt makeHfromRhoT\_edge} is
$(\rho h)'_\mathrm{edge}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advancing $\rho h$}
We update the enthalpy analogously to the species update in 
Section \ref{Advancing rhoX_k}.  The forcing term does not include reaction
source terms accounted for in {\bf React State}, and is the same
for all {\tt enthalpy\_pred\_type}s.
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = 
-\nabla\cdot\left\{\left \langle (\rho h) \right \rangle_\mathrm{edge}
 \left(\Ubt + w_0\eb_r\right)\right\} + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} + \psi  \enskip .
\end{equation}
where $\left \langle (\rho h) \right \rangle_\mathrm{edge}$ is the
edge state for $(\rho h)$ computed as listed in the final column of
table~\ref{table:pred:hoverview} for the given {\tt enthalpy\_pred\_type}
and {\tt species\_pred\_type}.
